### 2016-10-05 robust-software.tex
Adding ref to Steinmacher

\item
Point out that having tests of any kind makes it simpler for outsiders to contribute.

@@

>>>>

@@

Finally,
studies have found that the ease with which people can start making
contributions is a strong predictor of whether they will or not~\cite{steinmacher2015}.
By making it simpler for outsiders to contribute,
a test suite of any kind also makes it more likely that they will.
